Response to reviews of ``Quantifying the effects of single mutations on viral escape from broad and narrow antibodies to an H1 influenza hemagglutinin'' from \textit{Nature Microbiology}

### 2018-01-16 paper/NatureMicrobiologyReviews.tex
intro to reviewer response

Below we provide a detailed point-by-point response to the reviews.
As you will see, we have been able to clarify and address all the questions / concerns.

In conclusion, our paper has been rigorously evaluated by four expert reviewers, who all found it to be scientifically sound, raising only minor points that we have clarified in our response / revision.
The only question was whether our work was of sufficient impact for \textit{Nature Microbiology}, with the reviewers splitting about equally on this question.
The \textit{Nature Communications} policies read: ``While \textit{Nature} and Nature research journals strive to publish the highest impact research within these disciplines, \textit{Nature Communications} is committed to publishing important advances of significance to specialists within each field.''
Our study clearly meets these criteria, and so is suitable for \textit{Nature Communications}.

@@

@@

>>>>

Below we provide a detailed point-by-point response to the reviews.
As you will see, we have addressed all the questions / concerns.

In conclusion, our paper has been evaluated by four expert reviewers, who all found it to be scientifically sound, raising only minor points that we have clarified in our response / revision.
The only question was whether our work was of sufficient impact for \textit{Nature Microbiology}, with the reviewers splitting on this question.
The \textit{Nature Communications} policies read: ``While \textit{Nature} and Nature research journals strive to publish the highest impact research within these disciplines, \textit{Nature Communications} is committed to publishing important advances of significance to specialists within each field.''
Our study clearly meets these criteria from the evaluations of all reviewers, and so is suitable for \textit{Nature Communications}.

@@

{\color{black}
Thanks for selecting reviewers who cover the full spectrum of relevant expertise.}

@@

{\color{black}
We appreciate the fact that the reviewer find our work to be both technically sound and of high impact.}
